The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-04-18 paper/github_interview.tex
Fixed some typos.

\newpage

@@

\subsection*{Q: How is GitHub changing the way Open Source Software (OSS) is being developed today?}
GitHub moved the open source community away from a permission culture. Prior to GitHub contributing to an open source project was very difficult and often involved asking permission. By allowing people to fork a repository and make changes without asking for permission, GitHub has made contributing to someone else's project much easier than it has ever been. By submitting a Pull Request with suggested changes, project maintainers and contributors have a place to discuss changes to code that is already written and to refine it.

@@

Software Engineering is moving more towards the development models seen in industry. It's much more useful to students to learn how to use the tools that they will see in industry than it is to learn how to use learning management systems and the like. I encourage teachers to assign project work in teams so that students gain experience working together and navigating the issues that arrive in a collaborative environment. While it's far from standard practice, I'm seeing more and more teachers encouraging and even requiring the use of version control, code review, and automated testing. Most of these tools have been standard in industry for quite a while, but only recently have they made their way into the classroom thanks to services like GitHub lowering the learning curve substantially.

>>>>

\clearpage

@@

\subsection*{Q: How is GitHub changing the way Open Source Software (OSS) is being developed today?}
GitHub moved the open source community away from a permission culture. Prior to GitHub, contributing to an open source project was very difficult and often involved asking permission. By allowing people to fork a repository and make changes without asking for permission, GitHub has made contributing to someone else's project much easier than it has ever been. By submitting a Pull Request with suggested changes, project maintainers and contributors have a place to discuss changes to code that is already written and to refine it.

@@

Software Engineering is moving more towards the development models seen in industry. It's much more useful for students to learn how to use the tools that they will see in industry than it is to learn how to use learning management systems and the like. I encourage teachers to assign project work in teams so that students gain experience working together and navigating the issues that arrive in a collaborative environment. While it's far from standard practice, I'm seeing more and more teachers encouraging and even requiring the use of version control, code review, and automated testing. Most of these tools have been standard in industry for quite a while, but only recently have they made their way into the classroom thanks to services like GitHub lowering the learning curve substantially.

### 2013-04-18 paper/main.tex
Fixed some typos.

\subsubsection{Attributes}
\label{sec:attributes}
The individual \textit{Attribute} names, or the elements of $A^\prime$, are described below. For detailed summary statistics of these \textit{Attributes}, see Figure \ref{table:summary_stats}.\\\\
\noindent \textbf{\textit{Issues:}}
The number of issues posted to a repository's issue tracker.\footnote{https://github.com/blog/411-github-issue-tracker}

@@

Table \ref{table:summary_stats} describes summary statistics of the repository variables above. The most evident feature of the result is the large variance. In fact, for the set of tested variables $A$, each variable $A_j$ is observed to have a larger standard deviation than the variable mean.
\begin{equation}
\forall j \in A \colon \overline{j} < \sigma_{j}
\label{eq:variance}
\end{equation}
All measured variables demonstrated this characteristic.

@@

Spending large amounts of time and resources to participate is a detriment to knowledge-sharing in general, not just OSS development\cite{ardichvili2003motivation}. Because of this, we conclude that this permissive culture of knowlege-sharing that GitHub fosters represents an important change in the OSS process.

>>>>

\subsubsection{Attributes}
\label{sec:attributes}
The individual \textit{Attribute} names, or the elements of $A^\prime$, are described below. For detailed summary statistics of these \textit{Attributes}, see Table \ref{table:summary_stats}.\\\\
\noindent \textbf{\textit{Issues:}}
The number of issues posted to a repository's issue tracker.\footnote{https://github.com/blog/411-github-issue-tracker}

@@

Table \ref{table:summary_stats} describes summary statistics of the repository variables above. The most evident feature of the result is the large variance. In fact, for the set of tested variables $A$, each variable $A_j$ is observed to have a larger standard deviation than the variable mean:
\begin{equation}
\forall j \in A \colon \overline{j} < \sigma_{j}
\label{eq:variance}
\end{equation}
All measured variables demonstrated this characteristic.

@@

Spending large amounts of time and resources to participate is a detriment to knowledge-sharing in general, not just OSS development\cite{ardichvili2003motivation}. Because of this, we conclude that this permissive culture of knowlege-sharing that GitHub fosters represents an important change in the OSS process.\\
